Fifteen years of decentralization attempts

### 2014-03-23 paper.tex
Moved text out of itemize that didn't belong and improved the introduction

\section{Introduction}
	All feelings of privacy on telephones, mobile phones or the internet is an illusion. In recent years the need for privacy enhancing technology has become more apparent. Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.

	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and are being used in practice. One of the most important factors that impact anonymity in a communication system is the number of users. A sufficiently large numbers of users are required for a system to make guarantees about its ability to protect the privacy of its users. This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users. To support a large number of users, such a network has to be decentralized. A lack of decentralization would otherwise result in bottlenecks that places constraints on the number of users that can be active.

@@

			The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. Furthermore, it would alleviate a security concern. A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes. In a decentralized environment such an attack would be much more difficult. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.

@@

>>>>

\section{Introduction}
	All feelings of privacy on the internet, telephones or mail is an illusion. In recent years the need for privacy enhancing technology has become more apparent. Revealing government wrongdoings, such as in the case of WikiLeaks, or the ability to communicate freely in a censored environment are two major examples of why anonymous communication is important.

	Although much research has been done on anonymous internet communication, only few systems have been actually implemented and only one is actively being used in practice. One of the most important factors that impact anonymity in a communication system is the number of users. A sufficiently large numbers of users is required for a system to make guarantees about its ability to protect the privacy of its users. This makes it difficult to introduce a new anonymous internet system, due to the initial lack of users. To support a large number of users, such a network has to be decentralized. A lack of decentralization would otherwise result in bottlenecks that place constraints on the number of users.

@@

@@

		The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.
